### 2020-02-21 manuscript/ERL_global_C_review.Rmd
landscape orientation for C cycle diagrams

![**Fig. 8 | C cycle diagram for mature tropical broadleaf forests.** Presented are mean±std, where geographically distinct areas are treated as the unit of replication. All units are Mg C ha^-1^ yr^-1^ (fluxes) or Mg C ha^-1^ (stocks). Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.](tables_figures/Tropical broadleaf YOUNG.png)

![**Fig. 9 | C cycle diagram for mature temperate broadleaf forests.** Presented are mean±std, where geographically distinct areas are treated as the unit of replication. All units are Mg C ha^-1^ yr^-1^ (fluxes) or Mg C ha^-1^ (stocks). Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.](tables_figures/Temperate broadleaf YOUNG.png)

![**Fig. 10 | C cycle diagram for mature temperate deciduous forests.** Presented are mean±std, where geographically distinct areas are treated as the unit of replication. All units are Mg C ha^-1^ yr^-1^ (fluxes) or Mg C ha^-1^ (stocks). Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.](tables_figures/Temperate conifer YOUNG.png)

![**Fig. 11 | C cycle diagram for mature boreal forests.** Presented are mean±std, where geographically distinct areas are treated as the unit of replication. All units are Mg C ha^-1^ yr^-1^ (fluxes) or Mg C ha^-1^ (stocks). Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.](tables_figures/Boreal conifer YOUNG.png)

>>>>

\newpage
\blandscape
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 8 | C cycle diagram for young tropical broadleaf forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

  knitr::include_graphics("tables_figures/Tropical broadleaf YOUNG.png")
```

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 9 | C cycle diagram for young temperate broadleaf forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

  knitr::include_graphics("tables_figures/Temperate broadleaf YOUNG.png")
```

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 10 | C cycle diagram for young temperate conifer forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

  knitr::include_graphics("tables_figures/Temperate conifer YOUNG.png")
```

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 11 | C cycle diagram for young boreal conifer forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

  knitr::include_graphics("tables_figures/Boreal conifer YOUNG.png")
```
\elandscape
